Community Analysis

### 2022-04-18 R/08-community.Rmd
update Readme; prevent saving of phyloseq RData file

save(ps, file = 'ps.RData')
# Differential abundance test
corncob <- bbdml(formula = ASV2954 ~ treat,
                                 phi.formula = ~ 1,
                                 formula_null = ~ 1,
                                 phi.formula_null = ~ 1,
                                 test = "lrt", boot = TRUE,
                                 data = ps_fam_pas5_prev,
                                 fdr_cutoff = 0.05)
da_analysis <- differentialTest(formula = ~ treat,
                                 phi.formula = ~ 1,
                                 formula_null = ~ 1,
                                 phi.formula_null = ~ 1,
                                 test = "Wald", boot = FALSE,
                                 data = ps_fam_pas5_prev,
                                 fdr_cutoff = 0.05, B = 50)
plot(da_analysis, level = c("Family"))
da_analysis$significant_models
dt_data <- plot(da_analysis, level = c("Family"), data_only = TRUE)

>>>>

#save(ps, file = 'ps.RData')
# Differential abundance test
corncob <- bbdml(formula = ASV2954 ~ treat,
                                 phi.formula = ~ 1,
                                 formula_null = ~ 1,
                                 phi.formula_null = ~ 1,
                                 test = "lrt", boot = TRUE,
                                 data = ps_fam_pas5_prev,
                                 fdr_cutoff = 0.05)
da_analysis <- differentialTest(formula = ~ treat,
                                 phi.formula = ~ 1,
                                 formula_null = ~ 1,
                                 phi.formula_null = ~ 1,
                                 test = "Wald", boot = FALSE,
                                 data = ps_fam_pas5_prev,
                                 fdr_cutoff = 0.05, B = 50)
plot(da_analysis, level = c("Family"))
da_analysis$significant_models
dt_data <- plot(da_analysis, level = c("Family"), data_only = TRUE)
